Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-20 article.rnw
Remove a note about null coclassification expectation that is now addressed in the methods.
Add the Mantel tests to the results.

\newcommand\rsquarednum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\aicnum[1]{\num{#1}}
\newcommand\probnum[1]{\num[round-mode=places,round-precision=3]{#1}}

@@

Coclassification matrices for the row and column groupings are shown in \cref{fig:coclassification}.
In all, no pair of species can confidently be said to be coclassified, in the row or column groupings; no probability of coclassification exceeded \SI{75}{\percent}.
Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.
% DBS: As I have noted before, I'd like to know what the null expectation is for this before claiming confidence of being co-classified or not being co-classified. Firstly, I think that the random expectation is much lower than one might otherwise suspect. (For three species, it is already 2/5; for four species, it is 5/15.) Second, the conventional "ecological" null is actually that the probability is 0, in which case it doesn't take much co-classification probability to see the glass as half full and argue that grouping is a much more parsimonious approach than the contrary.

The structure of the coclassifications was very different in the row groups than in the column groups.
Most pairs of species which had a high probability of being coclassified in one grouping had a very low probability of being coclassified in the other grouping.
Only one pair of species had a relatively high probability of being coclassified in both groupings: \emph{D. pallidifrons} and \emph{D. sulfurigaster}.
Overall, more coclassification occurred in the row groupings than in the column groupings.
% DBS: In the network modularity literature, there is a nice measure of mutual information between two partitions. I wonder if we could exploit that here to give a quantitative measure of similarity between the two. Or we could just convert the two matrices to distance matrices and run a Procrustes to measure their similarity?

@@

>>>>

\newcommand\rsquarednum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\aicnum[1]{\num{#1}}
\newcommand\probnum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\cornum[1]{\num[round-mode=places,round-precision=3]{#1}}

\newcommand\mantelstat{\ensuremath{r_{\text{M}}}}

@@

Coclassification matrices for the row and column groupings are shown in \cref{fig:coclassification}.
In all, no pair of species can confidently be said to be coclassified, in the row or column groupings; no probability of coclassification exceeded \SI{75}{\percent}.
Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.

The structure of the coclassifications was very different in the row groups than in the column groups.
Most pairs of species which had a high probability of being coclassified in one grouping had a very low probability of being coclassified in the other grouping.
Only one pair of species had a relatively high probability of being coclassified in both groupings: \emph{D. pallidifrons} and \emph{D. sulfurigaster}.
Overall, more coclassification occurred in the row groupings than in the column groupings.
A Mantel test of the coclassification matrix for the rows against that for the columns shows that there is no significant correlation between the two ($\mantelstat=\cornum{\Sexpr{mantel_cor(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$).

@@

Neither the row nor column coclassification matrix was significantly correlated with a dissimilarity matrix based on species body size (column: $\mantelstat=\cornum{\Sexpr{mantel_cor(col_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(col_distance_matrix, body_weight_distance_matrix)}}$; row: $\mantelstat=\cornum{\Sexpr{mantel_cor(row_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(row_distance_matrix, body_weight_distance_matrix)}}$).
